---
title: "Analysis for [project name]"
author: "Your name(s) and the name of the program"
output:
  pdf_document:
    toc: yes
    number_sections: yes
    keep_tex: yes
  bookdown::html_document2:
    css: .formatting/grattan-style.css
    theme: lumen
    highlight: pygments
    toc: yes
    toc_depth: 2
    toc_float: no
    number_sections: yes
    df_print: kable
---

```{r logo, echo=FALSE}
# This adds the grattan logo to the document (cute)
htmltools::img(src = knitr::image_uri(file.path(".formatting", "logo", "GrattanLogo_left.png")), 
               alt = 'logo', 
               style = 'position:absolute; top:0; right:0; padding:10px; height:8%;')
```


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, 
                      warning = FALSE, 
                      message = FALSE)

source("R/00-setup.R") 

rebuild_data <- FALSE
```

# Preface {.unnumbered}

The template is segmented into sections, in which you read, transform, visualise and explain data analysis.
You don't have to do it this way. If you'd prefer to read all the data used in the project first, then create charts and outputs later, that's fine too.

Just remember that this is a good place to document your code as you write.
And, like your charts, you'll be able to export your documentation to a LaTeX report quickly by clicking `Knit -> Knit to pdfdocument`. 


# Section header

Sentence explaining the analysis in this section.

## Section subheader

Detail about analysis.

```{r chunk-label}
# some R code here
```

